\section{Evaluation of \Tool}
\label{sec:eva}

\subsection{Methodology}

\noindent{\textbf{Implementation and Experimental Platform.}}
We implement \Tool using LLVM-5.0.0~\cite{llvm}. 
All our experiments are conducted on a machine, 
with Intel Xeon(R) 4110 CPU and Linux 3.10.0 kernel.


\noindent{\textbf{Benchmarks.}}
We collect evaluated complexity problems from two sources. 
The first one is our studied complexity problems in Section~\ref{sec:study}.
We successfully reproduce 17 of them. 
Among them, six are extracted from original Java or JS programs, 
and we re-implement them using C/C++.
The reason is that our current implementation of \Tool can only work on C/C++ programs.
One is extracted from a very old version of Mozilla Firefox. 
We fail to build the original software, 
due to some missing dependent libraries. 
Our re-implementation is based on our thorough understanding of these complexity problems.
In our re-implementation, we maintain their original algorithms, 
data structures and caller-callee relationships. 
For other bugs in our study, 
we fail to use them in our experiments, because they depend on special hardware 
or software, which is not available to us. 
We fail to re-implement them, because their data structures are too complex. 


The second source is from Toddler project~\cite{Alabama}. 
Toddler is a dynamic technique that can detect inefficient loops in Java programs.
In total, developers confirmed 21 bugs detected by Toddler. 
All of them are re-implemented in C/C++ 
in following-up work~\cite{ldoctor}.
We use all the 21 re-implemented bugs in our evaluation.  


\input{section/tab_inhouse}